Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit

### 2016-09-02 paper/paper.tex
Add author and acknowledgements
Other mods

\begin{document}
\title{Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit}
\author{V. Veibell and R.S. Weigel}
\doublespacing
\maketitle

@@

Figure~\ref{fig:BzBinned} shows the the events of Figure~\ref{fig:HourlyAveragedRhoEvents} when separated by $B_z$ in the same manner as Figure~\ref{fig:BzBinnedDstEvents}.  The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to a larger peak in $\rho_{eq}$ than more negative $B_{z}$.  The rate of change of $\rho_{eq}$ also appears to be insensitive to $B_z$ for the time windows used to determine the separation.

@@

In recent years, various works have considered the influence of solar wind control and the geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\cite{Takahashi2006}; \cite{Denton2006}; \cite{Yao2008}; \cite{Takahashi2010}; \cite{Denton2016}).  The event studies show a possible relationship between $\rho_{eq}$ and solar wind and geomagnetic activity indicators such as $K_p$ and $D_{st}$ while correlation studies have generally found a very weak relationship.

@@

@@

>>>>

\begin{document}
\title{Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit}
\author{V. Veibell, R.S. Weigel, and R.E. Denton}
\doublespacing
\maketitle

@@

Figure~\ref{fig:BzBinned} shows the the events of Figure~\ref{fig:HourlyAveragedRhoEvents} when separated by $B_z$ in the same manner as Figure~\ref{fig:BzBinnedDstEvents}.  The largest difference occurs when the separation is performed after onset, with more positive $B_z$ leading to a larger peak in $\rho_{eq}$ than more negative $B_{z}$.  The rate of change of $\rho_{eq}$ also appears to be insensitive to the time windows used to determine the separation (before or after onset).

@@

In recent years, various works have considered the influence of solar wind control and the geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit, generally using event studies and linear correlations (\cite{Takahashi2006}; \cite{Denton2006}; \cite{Yao2008}; \cite{Takahashi2010}; \cite{Denton2011}; \cite{Denton2016}).  The event studies show a possible relationship between $\rho_{eq}$ and solar wind and geomagnetic activity indicators such as $K_p$ and $D_{st}$ while correlation studies have generally found a very weak relationship.

@@

%Based on a weak linear relationship between $\rho_{eq}$ and $B_z$, \cite{Denton2016} speculated that this may be a result of a closed magnetosphere being more conducive to plasmasphere refilling.

@@

\section{Acknowledgements}

Work at Dartmouth College was supported by NSF grant AGS-1105790
